A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-02-26 manuscript/manuscript.qmd
prelim render to send to RJG for review

format: 
  docx:
    fig-cap-location: top
    tbl-cap-location: top
    reference-doc: custom-reference-doc.docx
  pdf:
    fig-cap-location: top
    tbl-cap-location: top

@@

```{r}
#| label: tbl-criteria
#| tbl-cap: "Criteria to select eligible trials for emulation in ENCORE."
#| tbl-cap-location: top

@@

```{r}
#| label: tbl-rcts
#| tbl-cap: "Tentative list of randomized controlled trials (RCTs) considered for emulation."
#| tbl-cap-location: top

@@

```{r}
#| label: tbl-metrics
#| tbl-cap: "Visualization of agreement metrics example."

@@

```{r}
#| label: fig-process
#| fig-cap: "Systematic process to understand effectiveness claims of oncology trials using real-world evidence."
#| fig-cap-location: top
#| fig-width: 12

@@

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_1_process.png)

@@

```{r}
#| label: fig-initiators
#| fig-cap: "Example visualization of descriptive drug utilization analyses displaying a) initiation trends between compared regimens based on calendar time, b) cumulative rate of patients switching to another line of treatment."
#| fig-widh: 3
#| fig-height: 6

@@

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_2_utlization.png)

@@

```{r}
#| label: fig-balance
#| fig-cap: "Assessment of a) covariate balance and b) distributional balance of a prognostic score for overall survival before and after propensity score matching or weighting across multiple imputed datasets."
#| fig-widh: 4
#| fig-height: 7

@@

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_3_balance.png)

>>>>

format: 
  docx:
    fig-cap-location: top
    tbl-cap-location: top
    reference-doc: custom-reference-doc.docx
  pdf:
    fig-cap-location: top
    tbl-cap-location: top
    extra_dependencies: ["float"]
    keep-tex: true
    fig-pos: 'h'
    tbl-pos: 'h'

@@

```{r}
#| label: tbl-criteria
#| tbl-cap: "Criteria to select eligible trials for emulation in ENCORE."
#| tbl-cap-location: top
#| fig-pos: 'h'
#| tbl-pos: 'h'

@@

```{r}
#| label: tbl-rcts
#| tbl-cap: "Tentative list of randomized controlled trials (RCTs) considered for emulation."
#| tbl-cap-location: top
#| fig-pos: 'h'
#| tbl-pos: 'h'

@@

```{r}
#| label: tbl-metrics
#| tbl-cap: "Visualization of agreement metrics example."
#| fig-pos: 'h'
#| tbl-pos: 'h'

@@

```{r}
#| label: fig-process
#| fig-cap: "Systematic process to understand effectiveness claims of oncology trials using real-world evidence."
#| fig-cap-location: top
#| fig-width: 12
#| fig-pos: 'h'
#| tbl-pos: 'h'

@@

::: {.content-visible unless-format="pdf"}
[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_1_process.png)
:::

@@

```{r}
#| label: fig-initiators
#| fig-cap: "Example visualization of descriptive drug utilization analyses displaying a) initiation trends between compared regimens based on calendar time, b) cumulative rate of patients switching to another line of treatment."
#| fig-widh: 3
#| fig-height: 6
#| fig-pos: 'h'
#| tbl-pos: 'h'

@@

::: {.content-visible unless-format="pdf"}
[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_2_utlization.png)
:::

@@

```{r}
#| label: fig-balance
#| fig-cap: "Assessment of a) covariate balance and b) distributional balance of a prognostic score for overall survival before and after propensity score matching or weighting across multiple imputed datasets."
#| fig-widh: 4
#| fig-height: 7
#| fig-pos: 'h'
#| tbl-pos: 'h'

@@

::: {.content-visible unless-format="pdf"}
[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_3_balance.png)
:::
